---
title: "Clustered assginment"
author: "Yijun Shen"
date: "2/10/2022"
output: html_document
---

##Yijun Shen:
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(wooldridge)
library(multcomp)
library(reticulate)
library(knitr)
library(varhandle)
library(tidyverse)
library(plotly)
library(gapminder)
library(dplyr)
library(ggplot2)
library(tidyr)
library(readxl)
library(cowplot)
library(ggthemes)
library(lubridate)
library(ggplot2)
library(dplyr)
library(readr)
d1<-read.csv(file = "UPS_Merged_data_3.csv")
```



```{r }
d1 %>%
  mutate(stop_time)
summary(d1$over_70.x)
boxplot(d1$stop_time ~ d1$over_70.x, main="Between Package over 70 lb",
   xlab="Package Over 70 lb", ylab="Stop time")
tapply(X = d1$stop_time, INDEX = d1$over_70.x, FUN = mean)
tapply(X = d1$stop_time, INDEX = d1$over_70.x, FUN = sd)
smk.par.tab <- table(d1$stop_time,d1$over_70.x)
addmargins(smk.par.tab)
```

other graph

```{r}
ggplot(data = d1, aes(x=stop_time, y=over_70.x)) +
  geom_line(stat = "identity", color = "black") +
  geom_point(stat = "identity", color = "blue") +
  geom_area(fill = "red", alpha = 0.5) +
  labs(title = "Between Package over 70 lb",
   x="Package Over 70 lb", y="Stop time") +
                theme_minimal_hgrid() +
                theme(axis.text = element_text(face = "bold"),
                 plot.title = element_text(size = 18, face = "bold"),
                 axis.title = element_text(face = "bold", size = 14))
```

## Xiuyi

```{r}
data_merge <- d1
```

```{r}
summary(data_merge$del_pkgs)
boxplot(del_pkgs~date.x,data=data_merge, main="distribution of amount of package delivery",
   xlab="DATE", ylab="package delivered")
```
# transform the data type of date to as.Date
```{r}
data_merge$date.x <- as.Date(data_merge$date.x)
```
# overall commercial and residential proportion
```{r}
data_merge$rescom_stop.x <- as.factor(data_merge$rescom_stop.x)
levels(data_merge$rescom_stop.x) <- c("Residential","Commercial")
prop.table(table(data_merge$rescom_stop.x))
```

#filter the data
```{r}
pkg_filter <- data_merge %>% 
  select (date.x,del_pkgs, rescom_stop.x, stop_time) %>%
  filter(del_pkgs<=10 	)
print(nrow(data_merge))
print(nrow(pkg_filter))
```

# average package in commercial and residential
```{r}
pkg_filter %>%
  group_by(rescom_stop.x) %>%
  summarize(mean_package=mean(del_pkgs)) %>%
  pivot_longer(cols = last_col()) %>%
  pivot_wider(everything())  %>%
  mutate_if(is.numeric, ~round(., 3)) %>%
  kable()
```
# ggplot overall package deliver quantity and wait time 
```{r}
ggplot(pkg_filter , aes(x=del_pkgs, y = stop_time))+
  geom_point(color="red", alpha=.5 , position=position_jitter(w=0.2))+
  geom_smooth(method='lm')+ 
   ggtitle('package quantity vs stop time') +
 xlab('Q Package') +
  ylab('Stop Time')
```
# ggplot overall package deliver quantity and wait time classified by residential and commercial


```{r}
ggplot(pkg_filter , aes(x=del_pkgs, y = stop_time))+
  geom_point(color="red", alpha=.5)+
  geom_smooth(method='lm')+ 
  facet_grid(~rescom_stop.x, scales="free")+
   ggtitle('package quantity vs stop time by customer address type') +
 xlab('Q Package') +
  ylab('Stop Time')

``` 
#
```{r}
pkg_filter$package_count <- as.factor(pkg_filter$del_pkgs)
prop.table(table(pkg_filter$package_count))
```


```{r}
pkg_filter %>%
  select(package_count,stop_time)%>%
  group_by(package_count) %>%
  summarize(avg_stop=mean(stop_time),median_stop=median(stop_time)) %>%
  pivot_longer(cols = last_col()) %>%
  pivot_wider(everything())  %>%
  mutate_if(is.numeric, ~round(., 3)) %>%
  kable()
```

# overall regression
```{r}
reg<- lm(formula = stop_time ~ del_pkgs, data = pkg_filter)
coef(reg)
```
# Residential regression
```{r}
reg<- lm(formula = stop_time ~ del_pkgs, data = pkg_filter[pkg_filter$rescom_stop.x=='Residential',])
coef(reg)
```
# Commercial regression
```{r}
reg<- lm(formula = stop_time ~ del_pkgs, data = pkg_filter[pkg_filter$rescom_stop.x=='Commercial',])
coef(reg)
```
```{r}
print(cor(pkg_filter$del_pkgs, pkg_filter$stop_time, method = "pearson"))
```
The quantity of the package delivery is positively correlated with the stop time; the commercial shows a strong covariance value than the residential one

## Christina

```{r}
#merged%>%
  unique(d1$location_des.x)
```

```{r}
d1$loc_desc<-NULL
d1[d1$location_des.x != c("MET CUSTOMER", "OFFICE","RECEIVER","JANITOR","GUARD","CONCIERGE","DOOR PERSON","HOSTESS"),"loc_desc"]<-0
d1[d1$location_des.x==c("MET CUSTOMER", "OFFICE","RECEIVER","JANITOR","GUARD","CONCIERGE","DOOR PERSON","HOSTESS"), "loc_desc"]<-1
```

```{r}
d1$stop_time_larger_unit<-d1$stop_time*3600
```

```{r}
sum(d1$loc_desc==1)
sum(d1$loc_desc==0)
```

```{r}
NotMeetFrac<-sum(d1$loc_desc==0)/(sum(d1$loc_desc==0)+sum(d1$loc_desc==1))
MeetFrac<-sum(d1$loc_desc==1)/(sum(d1$loc_desc==0)+sum(d1$loc_desc==1))
NotMeetFrac
MeetFrac
```

```{r}
summary(d1$loc_desc)
```

```{r}
number<-c(sum(d1$loc_desc==0), sum(d1$loc_desc==1))
whether_meet<-c("NotMeet", "Meet")
df<-data.frame(whether_meet,number)
df

plot_ly(df, x=~whether_meet,y=~number,type="bar")
```


```{r}
w<-lm(stop_time_larger_unit~loc_desc, data=d1)
summary(w)
# s=46.4364+28.4373l
```

```{r}
cor(d1$loc_desc, d1$stop_time_larger_unit)
```

##Neel
```{r}
summary(d1$bonus.x)
noBonus <- sum(d1$bonus.x == 0)
bonus <- sum(d1$bonus.x == 1)
noBonusFrac <- noBonus/(noBonus + bonus)
bonusFrac <- bonus/(noBonus + bonus)

dataTwo <- d1 %>%
  group_by(date.x) %>%
  summarize(bonus <- sum(bonus.x == 1), noBonus <- sum(bonus.x == 0)) %>%
  rename(bonus = `bonus <- sum(bonus.x == 1)`, noBonus = `noBonus <- sum(bonus.x == 0)`) %>%
  summarize(date.x, bonus, noBonus, bonusFrac <- bonus/(noBonus + bonus), noBonusFrac <- noBonus/(noBonus + bonus))

dataTwo


cor(d1$bonus.x, d1$stop_time)
cor(d1$bonus.x, d1$stop_time_2)
```
There is no need to include bonus in the model because clearly, there is no consistent correlation with stop_time or stop_time_2.

## Workers that have 3 data points

```{r}
dataPoints <- d1 %>%
  group_by(unique) %>%
  summarize(total = n())

threePoints <- sum(dataPoints == 3)

twoPoints <- sum(dataPoints == 2)

onePoint <- sum(dataPoints == 1)


numPointsCount <- rbind(onePoint, twoPoints, threePoints)

total <- sum(threePoints + twoPoints + onePoint)

fracThree <- threePoints/total 
fracTwo <- twoPoints/total
fracOne <- onePoint/total

numPointsFrac <- rbind(fracOne, fracTwo, fracThree)

cbind(numPointsCount, numPointsFrac)
```

Unfortunately, most of the data is singular data points (60%), about 24% have two data points, and 16% have 3 data points. This isn't really panel data in this case because we don't observe the same employees over time for the most part.


##Marawan
## Setup

```{r}
data <- d1 %>%
  mutate(stop_time)
```

## removing stops = 0


```{r }
data %>% 
  filter(stop_start >= stop_complete)%>%
  nrow()

data %>%
  filter(stop_time_2 <= 0)%>%
  nrow()

data <- data %>%
  filter(stop_start < stop_complete, stop_time_2 > 0)
```

```{r }

#does time matter? 
data_timeOfDay <- data %>%
  select(stop_time_2, morning, afternoon, evening) %>%
  filter(na.rm = TRUE)
  
cor(data_subset, use="pairwise.complete.obs")



#cor(data_dateImpact, use = "pairwise.complete.obs")

data_subset_pckgQuant <- data %>%
  select(comvol.x,
resvol.x,
sig_req.x,
signature.x,
stop_time_2
)%>%
  filter(na.rm = TRUE)

cor(data_subset_pckgQuant, use="pairwise.complete.obs")

```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.


```{r}

#total unique drivers
data %>%
  filter(tolower(emp_job_desc.x) == "package driver")%>%
  distinct(emp_id.x)%>%
  nrow()

data %>%
  filter(tolower(emp_job_desc.x) == "full-time combination driver")%>%
  distinct(emp_id.x)%>%
  nrow()

#total unique districts
data %>%
  #distinct(dd.x)%>%
  group_by(dd.x)%>%
  summarise(total = n())

#unique dates
data %>%
  #distinct(date.x)%>%
  group_by(date.x)%>%
  summarise(total = n())



```





```{r}

data_dateImpact <- data %>%
  select(stop_time_2, date.x, emp_start_dt.x)%>%
  mutate(tenure = difftime(as.Date("date.x", format = "%y-%m-%d"), as.Date("emp_start_dt.x",format = "%y-%m-%d"),))

data_dateImpact



```
