---
title: "del_pkgs"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(dplyr)
library(reticulate)
library(knitr)
library(varhandle)
```

```{r}
data_merge <- d1
```

```{r}
summary(data_merge$del_pkgs)
boxplot(del_pkgs~date.x,data=data_merge, main="distribution of amount of package delivery",
   xlab="DATE", ylab="package delivered")
```
# transform the data type of date to as.Date
```{r}
data_merge$date.x <- as.Date(data_merge$date.x)
```
# overall commercial and residential proportion
```{r}
data_merge$rescom_stop.x <- as.factor(data_merge$rescom_stop.x)
levels(data_merge$rescom_stop.x) <- c("Residential","Commercial")
prop.table(table(data_merge$rescom_stop.x))
```

#filter the data
```{r}
pkg_filter <- data_merge %>% 
  select (date.x,del_pkgs, rescom_stop.x, stop_time) %>%
  filter(del_pkgs<=10 	)
print(nrow(data_merge))
print(nrow(pkg_filter))
```

# average package in commercial and residential
```{r}
pkg_filter %>%
  group_by(rescom_stop.x) %>%
  summarize(mean_package=mean(del_pkgs)) %>%
  pivot_longer(cols = last_col()) %>%
  pivot_wider(everything())  %>%
  mutate_if(is.numeric, ~round(., 3)) %>%
  kable()
```
# ggplot overall package deliver quantity and wait time 
```{r}
ggplot(pkg_filter , aes(x=del_pkgs, y = stop_time))+
  geom_point(color="red", alpha=.5 , position=position_jitter(w=0.2))+
  geom_smooth(method='lm')+ 
   ggtitle('package quantity vs stop time') +
 xlab('Q Package') +
  ylab('Stop Time')
```
# ggplot overall package deliver quantity and wait time classified by residential and commercial


```{r}
ggplot(pkg_filter , aes(x=del_pkgs, y = stop_time))+
  geom_point(color="red", alpha=.5)+
  geom_smooth(method='lm')+ 
  facet_grid(~rescom_stop.x, scales="free")+
   ggtitle('package quantity vs stop time by customer address type') +
 xlab('Q Package') +
  ylab('Stop Time')

``` 
#
```{r}
pkg_filter$package_count <- as.factor(pkg_filter$del_pkgs)
prop.table(table(pkg_filter$package_count))
```


```{r}
pkg_filter %>%
  select(package_count,stop_time)%>%
  group_by(package_count) %>%
  summarize(avg_stop=mean(stop_time),median_stop=median(stop_time)) %>%
  pivot_longer(cols = last_col()) %>%
  pivot_wider(everything())  %>%
  mutate_if(is.numeric, ~round(., 3)) %>%
  kable()
```

# overall regression
```{r}
reg<- lm(formula = stop_time ~ del_pkgs, data = pkg_filter)
coef(reg)
```
# Residential regression
```{r}
reg<- lm(formula = stop_time ~ del_pkgs, data = pkg_filter[pkg_filter$rescom_stop.x=='Residential',])
coef(reg)
```
# Commercial regression
```{r}
reg<- lm(formula = stop_time ~ del_pkgs, data = pkg_filter[pkg_filter$rescom_stop.x=='Commercial',])
coef(reg)
```
```{r}
print(cor(pkg_filter$del_pkgs, pkg_filter$stop_time, method = "pearson"))
```
The quantity of the package delivery is positively correlated with the stop time; the commercial shows a strong covariance value than the residential one
